---
title: "Animation of a simulation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Animation of a simulation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CHESS)
library(gganimate)
```


## Taking of snapshots during the simulation
During the simulation snapshots can be taken at given time points by passing these to the `new_simulation` constructor as follows:

```{r create_simulation, results='hide'}
sim = new_simulation(50, snapshot_times = 1:30^2) # takes snapshots at `snapshot_times`
```

## Animation of snapshots

Snapshots taken during the simulation can then be converted to a *gganim object* by calling the `plot_animation_CHESS_S3` function: 

```{r render_animation, fig.height=3, fig.height=3.8}
anim = animate(sim) # get gganim object
animate(anim) # render animation 
```


There are a couple of optional arguments that can be passed to the `animate` function. These are shortly demonstrated below. For more details please refer to the corresponding man page (see `?animate.CHESS_S3`). 

### Different scaling of the axis labels
```{r fig.height=3, fig.height=3.8}
animate(sim, mm_per_dot = 0.01) # 
```

### Different background color of the simulated space
```{r fig.height=3, fig.height=3.8}
animate(sim, background_color = "gray5") # 
```

### Coloring of cells by different attributes
```{r fig.height=3, fig.height=3.8}
animate(sim, color_by = 'type') # 
```
